

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
\documentclass[manuscript,screen,review]{acmart}

\else
\documentclass{article}
\input{usepackage}
\addbibresource{sample.bib} %Import the bibliography file

\fi
\begin{document}

\newcommand{\commentt}[1]{\textcolor{blue}{ \textbf{[COMMENT]} #1}}
\newcommand{\ctt}[1]{\commentt{#1}}
\newcommand{\prb}[1]{ \mathbf{Pr} \left[ {#1} \right]}
\newcommand{\onotation}[1]{\(\mathcal{O} \left( {#1}  \right) \)}
\newcommand{\ona}[1]{\onotation{#1}}
%\newcommand{\PSI}{{\ket{\psi}}}
%\newcommand{\LESn}{\ket{\psi_n}}
%\newcommand{\LESa}{\ket{\phi_n}}
%\newcommand{\LESs}{\frac{1}{\sqrt{n}}\sum_{i}{\ket{\left(0^{i}10^{n-i}\right)^{n}}}}
%\newcommand{\Hn}{\mathcal{H}_{n}}
%\newcommand{\Ep}{\frac{1}{\sqrt{2^n}}\sum^{2^n}_{x}{ \ket{xx}}}
%\newcommand{\HON}{\ket{\psi_{\text{honest}}}}
%\newcommand{\Lemma}{\paragraph{Lemma.}}
\newcommand{\Cpa}{[n, \rho n, \delta n]}
%\setlength{\columnsep}{0.6cm}
\newcommand{\Jvv}{ \bar{J_{v}} } 
\newcommand{\Cvv}{ \tilde{C_{v}} } 

\newcommand{\Gz}{ G_{z}^{\delta} } 
\newcommand{ \Tann } {  \mathcal{T}\left( G, C_0 \right) }
\newcommand{\ireducable}{ireducable \hyperref[ire]{[\ref{ire}]} }
\newcommand{\cutUU}{E(U_{-1} \bigcup U_{+1} ,U)} 
\newcommand{\wcutUU}{w\left( E(U_{-1} \bigcup U_{+1} ,U)  \right)}
\newcommand{\testgo}{  \mathcal{T}\left(J, q , C_{0}\right) } 

\newcommand{\duC}{\left( C_{A}^{\perp}\otimes C_{B}^{\perp} \right)^{\perp}}
\newcommand{\duduC}{\left( C_{A}\otimes C_{B}\right)^{\perp}}
\title{Removing The $w$-Robustness Assumptions.} 
\author{David Ponarovsky}

\ifdefined\ACM
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}
\else
\maketitle
\fi
\input{abstract}
\ifdefined\ACM
\maketitle
\fi
%\begin{multicols*}{2}
\input{preamble}
    \input{backgroud}

 \subsection{Tanner testability.} This subsection will explain why testability is so hard to achieve. Let $C$ be a good Tanner expander code as defined above. And consider an arbitrary vertex $u \in V$ and arbitrary restriction of $C_{0}$, $h$. Now define $\tilde{C}$ as the code obtained by requiring all the restrictions of $C$ except $h$ on $u$. That it, $u$ is satisfied if his local view satisfies all the $C_{0}$ restrictions apart from $h$.
  Also, for convenience, denote the small code $u$ enforces on his local view by $C_{0}^{u}$. Let us assume that the distance of $C_{0}^{u}$ is at least $\delta\Delta$. 
  Then, by repeating almost exactly the steps above with caution, one could prove that $\tilde{C}$ also has a linear distance. 


  Assume that $\tilde{C} \neq C \Rightarrow$ there exists $x\in \tilde{C} / C$. By definition, for any $v\in V / \{u\}$ it holdes that $x|_{v} \in C_{0}$. Hence, the assumption that $ x \notin C$  implies $x|_{u} \notin C_{0}$ So, clearly, $x$ fails at a constant number of $C$'s checks. On the other hand, the closest codeword $y \in C$ to $x$ is also a codeword of $\tilde{C}$ as $y|_{v} \in C_{0}$ for every $v\in V$.  Hence:
  \begin{equation*}
    \begin{split}
      d\left( x,C \right) &= d\left( x,y \right) \ge d\left( \tilde{C} \right) =\Theta\left( n \right)
    \end{split}
  \end{equation*}
  Even if a linear number of bits needed to be flipped to correct $x$, only a single check observes that $x$ is indeed an error.
  
  \section{Construction}
  \subsection{Almost LTC With Zero Rate}
  \begin{definition}[The Disagreement Code] Given a Tanner code $C = \Tann$, define the code $C_{\oplus}$ to contain all the words equal to the formal summation $ \sum_{v \in V\left( G \right)} {c_{v} }$ when $c_{v}$ is an assignment of a codeword $ c_{v} \in C_0 $  on the edges of the vertex $ v \in V\left( G \right)$.
  We call to such code the \textbf{disagreement code} of $C$, as edges are set to 1 only if their connected vertices contribute to the summation codewords that are different on the corresponding bit to that edge. In addition, we will call to any contribute $c_v$, the \textbf{suggestion} of $v$. And notice that by linearity, each vertex suggests, at most, a single suggestion.   

  Finally, given a bits assessment $x \in \mathbb{F}_{2}^{E}$ over the edges of $G$, we will denote by $x^{\oplus} \in C_{\oplus} $ the codeword which obtained by summing up suggestions set such each vertex suggests the closet codeword to his local view. Namely, for each $v \in V$ define:   
  \begin{equation*}
    \begin{split}
      c_{v} & \leftarrow \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } \ \ \forall v\in V   \\
      x^{\oplus} & \leftarrow \sum_{v \in V}{c_{v}} 
    \end{split}
  \end{equation*}
  We will think about $x^{\oplus}$ as the disagreement between the vertices over $x$. 

\end{definition}

\begin{lemma}[Linearity Of The Disagreement] \label{lemma:lin} Consider the code $C = \Tann$. Let $ x \in \mathbb{F}_{2}^{E}$ then for any $ y \in C$ it holds that: 
  \begin{equation*}
    \begin{split}
      \left( x + y  \right)^{\oplus} = \left( x  \right)^{\oplus} 
    \end{split}
  \end{equation*}
\end{lemma}
  \begin{proof} Having that $y \in C$ followes $y|_v \in C_{0}$ and therefore $\arg_{ \tilde{c} \in C_{0}} \min{ d( z  , \tilde{c} ) } = y|_{v} + \arg_{ \tilde{c} \in C_{0}} \min{ d( z, \tilde{c} + y|_{v} ) } $, Hence the suggestion made by vertrx $v$ is: 
  \begin{equation*}
    \begin{split}
      c_{v}\leftarrow &  \arg_{ \tilde{c} \in C_{0}} \min{ d( (x+y)|_{v}  , \tilde{c} ) } \\
      \leftarrow &  y|_{v} +  \arg_{ \tilde{c} \in C_{0}} \min{ d( (x+y)|_{v}  , \tilde{c} + y|_{v} ) } \\
      \leftarrow &  y|_{v} +  \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } 
    \end{split}
  \end{equation*}
  It follows that: 

  \begin{equation*}
    \begin{split}
      \left( x + y \right)^{\oplus} =& \sum_{v\in V}{c_{v}} = \sum_{v \in V}{y|_{v}} + \sum_{v\in V}{ \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } } \\ 
      =& y^{\oplus} + x^{\oplus} = x^{\oplus}
    \end{split}
  \end{equation*}
  When the last transition follows immediately by the fact that $y \in C$ and therefore any pair of connected vertices contribute the same value for their associated edge \end{proof}

  \begin{definition} Let $C = \Tann$. We say that $x \in C_{\oplus}$ is \textbf{reducable} if there exists a vertex $v$ and a small codeword $c_v$, for which, adding the assignment of $c_v$ over the $v$'s edges to $x$ decreases the weight. Namely, $|x + c_{v}| < |x|$. If $x \in C_{\oplus}$ is not a reducable codeword then we say that $x$ is \textbf{ireducable} \label{ire}. \end{definition}

  \begin{theorem*}[Theorem 1] There exist a constant $\alpha > 0$ and an infinte family of Tanner Codes $C = \Tann$ such that any \ireducable codeword $x$ of a coresponding disagreement code $x \in C_{\oplus}$ at length $n$, weight at least $\alpha n$. \end{theorem*}


  \paragraph{Proof.} By induction over the number of vertices $V^\prime \subset V$, which suggest a nontrivial codeword to $x$. Base, assume that a single vertex $v \in V$ suggests a nontrivial codeword $c_{v} \in C_{0}$. Then it's clear that $x = c_{v}$. And therefore, we have that $|x +c_{v}| = 0 < |x|$.

  \paragraph{}

  Assume the correctness of the argument for every codeword defined by at most $m$ nontrivial suggestions made by $V^\prime \subset V$. And consider the graph $\left( V^\prime, E^\prime \right)$ induced by them. If the graph has more than a single connectivity component, then any of them is also a codeword of $C_{\oplus}$  but composed of at most $m-1$ nontrivial suggestions. Therefore, by the assumption, we could find a vertex $v$ and a proper small codeword $c_v \in C_0 $, such that the addition of the suggestion will decrease the weight of the codeword defined on that component and therefore decrease the total weight of $x$.

  So, we can assume that the vertices in $V^\prime$ compose a single connectivity component. Let be $x|_{v} \in \mathbb{F}_{2}^{\Delta}$ the bits of $x$ on the indices corresponding to $v$'s edges. For any $S \subset E$, define $w_{S}\left( x \right)$ as the weight that $x$ induces over $S$. Sometimes we will refer to $w_{S}\left( x \right)$ as the \textbf{flux} induced by $x$ over $S$.

  \paragraph{}

  The genreal idea of the proof is to show that if the distance of the small code is large ($ \ge \frac{2}{3}$ ) and $x$ is \ireducable codeword then there exist an indepandent subset of vertices $U \subset V^{\prime}$, at linear size, that induce a significant flux over $E/E^{\prime}$. If $U$ has linear size than also $x$ has a linear size, And if not, Then we will show that no serious interface has been occurred. ~\cref{claim:deg} and ~\cref{claim:tree-size} state that if one is willing to hide an ireducable \hyperref[ire]{[\ref{ire}]} error then he has to touch at least a linar number of verties. ~\cref{claim:flu1} and  ~\cref{claim:flu2} quanitify the flux that induced by such errors. 

\begin{claim}\label{claim:deg} For any $v \in V^\prime$ and corresponded suggestion $c_{v}$ it holds that: $w_{E^\prime}\left( c_{v} \right) \ge \frac{1}{2}\delta_{0}\Delta$. \end{claim}
  \begin{proof} Notice that any edge of $E$ connected only to a single vertex in $V^\prime$ equals the corresponding bit in the original suggestion made by $c_{v}$. Hence for every $v\in V^\prime$, it holds that: 
\begin{equation*}
      \begin{split}
	    w_{E / E^\prime}\left(x|_{v}\right) = w_{E / E^\prime}\left(c_{v}\right) \Rightarrow  w_{E / E^\prime}\left(x|_{v}\right) \le | x \cap c_{v} |
      \end{split}
    \end{equation*}
     Now consider the weight of $x + c_{v}$, By the assumption that $x$ is ireducable code word of $c_{\oplus}$ we have that: 
  
 \begin{equation*}
    \begin{split}
       |x + c_{v}| & = |x| + |c_{v}| - 2|x \cap c_{v}| > |x| \\
       \Rightarrow &   |x \cap c_{v}|  < \frac{1}{2} |c_{v}| \\
      w_{E^\prime}\left( c_{v} \right) &= |c_{v}| - w_{E / E^\prime}\left( c_{v} \right) =  |c_{v} | - w_{E / E^\prime}\left( x|_{v} \right) \\ 
      & \ge | c_{v} | - | x \cap c_{v} |  \ge \frac{1}{2}|c_{v}| = \frac{1}{2}\delta_{0}\Delta 
    \end{split}
  \end{equation*}
  \end{proof}

  Consider an arbitrary vertex $r \in V^\prime$, and consider the DAG obtained by the BFS walk over the subgraph $\left(V^\prime, E^\prime \right)$ starting at $r$. Denote this directed tree by $T$.

%Let $g$ be the girth of the graph and consider a layer $U$ in $T$ at height $h\left( U \right)$ satisfies the inequality $ h\left( U \right) < \frac{1}{2}g + l$ for some integer $l$.
  %\begin{adjustbox}{width=150pt}%\columnwidth}
%\begin{figure*}[t]%{width=150pt} %0.3\textwidth}

%\end{figure*}
%\end{adjustbox} 
  \begin{claim} \label{claim:tree-size} The size of $T$ is at least:
  \begin{equation*}
    \begin{split}
      |T| & \ge \left( \frac{1}{4}\delta_{0} - \frac{\lambda}{\Delta} \right)n 
    \end{split}
  \end{equation*}
\end{claim}
\begin{proof}By~\cref{claim:deg}  any $v \in T$ the degree of $v$ is at least $\frac{1}{2}\delta_{0}\Delta$ we have that: $E\left( T,T \right) \ge \frac{1}{2}\cdot \frac{1}{2}\delta_{0}\Delta |T|$. Combine the Mixining Expander Lemma we obtain:
  \begin{equation*}
    \begin{split}
      \frac{1}{4}\delta_{0}\Delta |T| & \le \frac{\Delta}{n}|T|^2  + \lambda|T| \\ 
      \Rightarrow & \left( \frac{\Delta}{n}|T| + \lambda -  \frac{1}{4}\delta_{0}\Delta \right)|T| \ge 0 \\ 
      \Rightarrow & |T| \ge \left( \frac{1}{4}\delta_{0} - \frac{\lambda}{\Delta} \right)n 
    \end{split}
  \end{equation*}
  \end{proof}
 %
 %  \begin{claim} There is a constant $\gamma > 0 $ such for any  $S \subset T$ it holds that:  
 %  \begin{equation*}
 %    \begin{split}
 %      \frac{\lambda}{\Delta} \le \gamma\left( 1 - \frac{1}{2}\delta_{0} \right)\frac{|S|}{|T|}
 %    \end{split}
 %  \end{equation*}
 %
 %  \begin{proof} Recall that the second largest eigenvalue 
 %
 %  Denote by $x|_{U}$ the bits of $x\in C$ correspond to the edges connected to at least one vertex in $U$. And denote by $w_{E/E^{\prime}}\left( x|_{U} \right)$ the weight induced by the $x|_{U}$ over the edges in $E/E^\prime$.
   \input{flux.tex}
   \input{goodltc.tex}
   \input{quant.tex}
   \input{decoder.tex}
  %\end{adjustbox}
%\end{figure*}
%\end{multicols*}
\printbibliography 
\end{document}

 



